Manuscript analyses

### 2024-04-03 cilta_cel/Manuscript analyses.Rmd
Update data for analysis

---
title: "Manuscript analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

@@

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
id_to_modify_neurotox <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))

>>>>

---
title: "Manuscript analyses"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output:
  word_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options:
  chunk_output_type: console
---

@@

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023_modifiedCCL_04032024.xlsx"),
                    sheet = "APHERESIS")
id_to_modify_neurotox <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))
